Testing Charts: viewers' perceptual accuracy in surveys

### 2023-07-21 SDSS-2023/testing-charts-accuracy.qmd
massaging tables

dframe %>% 
  dplyr::select(level, task, chart, estimate, std.error, letters) %>%
  mutate(
    task = ifelse(task=="ab", "Unaligned", "Aligned")
  ) %>%
  group_by(task) %>%
  mutate(
    ci_low = exp(estimate-1.96*std.error),
    ci_high = exp(estimate+1.96*std.error),
    estimate = exp(estimate)
  ) %>%
  tidyr::pivot_wider(
        id_cols = c(task, chart),
        names_from = level,
        values_from = c(estimate, ci_low, ci_high, letters)
      ) %>%
  gt() %>%
  tab_header(title = "Odds of accuracy by task and chart type") %>%
  fmt_number(
    everything(),
    decimals=2
  ) %>%
  cols_merge(
    columns = c("estimate_correct | same or wrong", "ci_low_correct | same or wrong",
                "ci_high_correct | same or wrong", "letters_correct | same or wrong"),
    pattern = "<<{1}>><< [{2}, {3}]>><< {4}>>"
  ) %>%
  cols_merge(
    columns = c("estimate_correct or same | wrong", "ci_low_correct or same | wrong",
                "ci_high_correct or same | wrong", "letters_correct or same | wrong"),
    pattern = "<<{1}>><< [{2}, {3}]>><< {4}>>"
  ) %>%
  tab_options(
    column_labels.font.weight = "bold",
    row_group.font.weight = "bold"
  ) %>%
  cols_label(
    .list = c(
      "chart" = "",
      "estimate_correct | same or wrong" = "correct | same or wrong",
      "estimate_correct or same | wrong" = "correct or same | wrong"
    )
  )
```

@@

coefs_clean(coefs_cd_correct) %>% mutate(task = "Aligned", correct="correct") %>%
 rbind(
  coefs_clean(coefs_ab_correct) %>% mutate(task = "Unaligned", correct="correct")
 ) %>%
 rbind(
  coefs_clean(coefs_cd_correct_same) %>% mutate(task = "Aligned", correct="not wrong")
 ) %>%
 rbind(
  coefs_clean(coefs_ab_correct_same) %>% mutate(task = "Unaligned", correct="not wrong")
 ) %>%
 dplyr::select(-std.error, -statistic) %>%
 mutate(
  p.value = ifelse (p.value <  0.001, "***",
      ifelse (p.value <  0.01, "**",
             ifelse (p.value < 0.05, "*",
                    ifelse (p.value < 0.1, ".", ""))))
 ) %>%
 group_by(variable) %>%
 pivot_wider(
    id_cols = c(term, variable),
    names_from = c(task, correct),
    values_from = c(estimate, ci_low, ci_high, p.value),
  ) %>% 
 gt() %>%
  tab_header(title = "Odds of accuracy by task and demographics of respondents") %>%
  tab_footnote("Signif. codes:  0 `***' 0.001 `**' 0.01 `*' 0.05 `.' 0.1 ` ' 1") %>%
 tab_options(
   column_labels.font.weight = "bold",
   row_group.font.weight = "bold",
   data_row.padding.horizontal = px(5),
   page.orientation = "landscape"
 ) %>%
  fmt_number(
    decimals=2
  ) %>%
  cols_width(
    1~px(50),
    contains("p.value") ~ px(10)
  ) %>%
  cols_align(
    align = "left",
    columns = contains("p.value")
  ) %>%
  cols_merge(
    columns = contains("ci") & contains("_Aligned_correct"),
    pattern = "<< [{1}, {2}]>>"
  ) %>%
  cols_merge(
    columns = contains("ci") & contains("_Aligned_not"),
    pattern = "<< [{1}, {2}]>>"
  ) %>%
  cols_move_to_end(contains("_Aligned_")) %>%
  tab_spanner(
    label = "correct | same or wrong",
    columns = contains("_Aligned_correct")
  )  %>%
  tab_spanner(
    label = "correct or same | wrong",
    columns = contains("_Aligned_not")
  ) %>%
  tab_spanner(
    label = "Aligned tiles",
    columns = contains("_Aligned_"),
    spanners = c("correct | same or wrong", "correct or same | wrong")
  ) %>%
  cols_move_to_end(contains("_Unaligned_")) %>%
  cols_merge(
    columns = contains("ci") & contains("_Unaligned_correct"),
    pattern = "<< [{1}, {2}]>>"
  ) %>%
  cols_merge(
    columns = contains("ci") & contains("_Unaligned_not"),
    pattern = "<< [{1}, {2}]>>"
  ) %>%
  tab_spanner(
    label = "correct | same or wrong ",
    columns = contains("_Unaligned_correct")
  )  %>%
  tab_spanner(
    label = "correct or same | wrong ",
    columns = contains("_Unaligned_not")
  ) %>%
  tab_spanner(
    label = "Unaligned tiles",
    columns = contains("_Unaligned")
  ) %>%
   cols_label(
    .list = c(
      "estimate_Aligned_correct" = "Est.",
      "ci_low_Aligned_correct" = "          [95% CI]",
      "p.value_Aligned_correct" = " ",
      "estimate_Aligned_not wrong" = "Est.",
      "ci_low_Aligned_not wrong" = "          [95% CI]",
      "p.value_Aligned_not wrong" = " ",
      "estimate_Unaligned_correct" = "Est.",
      "ci_low_Unaligned_correct" = "          [95% CI]",
      "p.value_Unaligned_correct" = " ",
      "estimate_Unaligned_not wrong" = "Est.",
      "ci_low_Unaligned_not wrong" = "          [95% CI]",
      "p.value_Unaligned_not wrong" = " "
    )
  )

>>>>

dframe %>% 
  dplyr::select(level, task, chart, estimate, std.error, letters) %>%
  mutate(
    task = ifelse(task=="ab", "Unaligned", "Aligned")
  ) %>%
  group_by(task) %>%
  mutate(
    ci_low = exp(estimate-1.96*std.error),
    ci_high = exp(estimate+1.96*std.error),
    estimate = exp(estimate)
  ) %>%
  tidyr::pivot_wider(
        id_cols = c(task, chart),
        names_from = level,
        values_from = c(estimate, ci_low, ci_high, letters)
      ) %>%
  gt() %>%
  tab_header(title = "Odds of accuracy by task and chart type") %>%
  fmt_number(
    everything(),
    decimals=2
  ) %>%
  cols_merge(
    columns = contains("ci") & contains("same or wrong"),
    pattern = "<< [{1}, {2}]>>"
  ) %>%
  tab_spanner(
    label = "correct | same or wrong",
    columns =  c("estimate_correct | same or wrong", "ci_low_correct | same or wrong",
                 "letters_correct | same or wrong")
  ) %>%
  cols_merge(
    columns = contains("ci") & contains("correct or same"),
    pattern = "<< [{1}, {2}]>>"
  ) %>%
  tab_spanner(
    label = "correct or same | wrong",
    columns =  c("estimate_correct or same | wrong", "ci_low_correct or same | wrong",
                "letters_correct or same | wrong")
  ) %>%
  tab_options(
    column_labels.font.weight = "bold",
    row_group.font.weight = "bold"
  ) %>%
  cols_label(
    .list = c(
      "chart" = "",
      "estimate_correct | same or wrong" = "correct | same or wrong",
      "estimate_correct or same | wrong" = "correct or same | wrong",
      "estimate_correct or same | wrong" = "Est.",
      "ci_low_correct or same | wrong" = "          [95% CI]",
      "letters_correct or same | wrong" = " ",
      "estimate_correct | same or wrong" = "Est.",
      "ci_low_correct | same or wrong" = "          [95% CI]",
      "letters_correct | same or wrong" = " "
    )
  ) 
```

@@

coefs_clean(coefs_cd_correct) %>% mutate(task = "Aligned", correct="correct") %>%
 rbind(
  coefs_clean(coefs_ab_correct) %>% mutate(task = "Unaligned", correct="correct")
 ) %>%
 rbind(
  coefs_clean(coefs_cd_correct_same) %>% mutate(task = "Aligned", correct="not wrong")
 ) %>%
 rbind(
  coefs_clean(coefs_ab_correct_same) %>% mutate(task = "Unaligned", correct="not wrong")
 ) %>%
 dplyr::select(-std.error, -statistic) %>%
 mutate(
  p.value = ifelse (p.value <  0.001, "***",
      ifelse (p.value <  0.01, "**",
             ifelse (p.value < 0.05, "*",
                    ifelse (p.value < 0.1, ".", ""))))
 ) %>%
 group_by(variable) %>%
 pivot_wider(
    id_cols = c(term, variable),
    names_from = c(task, correct),
    values_from = c(estimate, ci_low, ci_high, p.value),
  ) %>% 
 gt() %>%
  tab_header(title = "Odds of accuracy by task and demographics of respondents") %>%
  tab_footnote("Signif. codes:  0 `***' 0.001 `**' 0.01 `*' 0.05 `.' 0.1 ` ' 1") %>%
 tab_options(
   column_labels.font.weight = "bold",
   row_group.font.weight = "bold",
   data_row.padding.horizontal = px(5),
   page.orientation = "landscape"
 ) %>%
  fmt_number(
    decimals=2
  ) %>%
  cols_width(
    1~px(50),
    contains("p.value") ~ px(10)
  ) %>%
  cols_align(
    align = "left",
    columns = contains("p.value")
  ) %>%
  cols_merge(
    columns = contains("ci") & contains("_Aligned_correct"),
    pattern = "<< [{1}, {2}]>>"
  ) %>%
  cols_merge(
    columns = contains("ci") & contains("_Aligned_not"),
    pattern = "<< [{1}, {2}]>>"
  ) %>%
  cols_move_to_end(contains("_Aligned_")) %>%
  tab_spanner(
    label = "correct | same or wrong",
    columns = contains("_Aligned_correct")
  )  %>%
  tab_spanner(
    label = "correct or same | wrong",
    columns = contains("_Aligned_not")
  ) %>%
  tab_spanner(
    label = "Aligned tiles",
    columns = contains("_Aligned_"),
    spanners = c("correct | same or wrong", "correct or same | wrong")
  ) %>%
  cols_move_to_end(contains("_Unaligned_")) %>%
  cols_merge(
    columns = contains("ci") & contains("_Unaligned_correct"),
    pattern = "<< [{1}, {2}]>>"
  ) %>%
  cols_merge(
    columns = contains("ci") & contains("_Unaligned_not"),
    pattern = "<< [{1}, {2}]>>"
  ) %>%
  tab_spanner(
    label = "correct | same or wrong ",
    columns = contains("_Unaligned_correct")
  )  %>%
  tab_spanner(
    label = "correct or same | wrong ",
    columns = contains("_Unaligned_not")
  ) %>%
  tab_spanner(
    label = "Unaligned tiles",
    columns = contains("_Unaligned")
  ) %>%
   cols_label(
    .list = c(
      "term" = " ",
      "estimate_Aligned_correct" = "Est.",
      "ci_low_Aligned_correct" = "          [95% CI]",
      "p.value_Aligned_correct" = " ",
      "estimate_Aligned_not wrong" = "Est.",
      "ci_low_Aligned_not wrong" = "          [95% CI]",
      "p.value_Aligned_not wrong" = " ",
      "estimate_Unaligned_correct" = "Est.",
      "ci_low_Unaligned_correct" = "          [95% CI]",
      "p.value_Unaligned_correct" = " ",
      "estimate_Unaligned_not wrong" = "Est.",
      "ci_low_Unaligned_not wrong" = "          [95% CI]",
      "p.value_Unaligned_not wrong" = " "
    )
  )
